---
title: "LTMLE Project Outputs"
author: "Laura Aleksonis, Siyaa Bhargava, Xhemka Elezi"
date: "2026-04-18"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = TRUE}
#install.packages('ggplot2')
library(ggplot2)
cat('Packages retrieved!')
```

# Retrieval of Data and Results

The working directory should be set to a folder containing all relevant items,
including a folder named "Datasets" where the dataset of interest resides.

```{r, message = FALSE}
path <- 'LTMLE_Testing_2.R'
source(path)
cat('Data retrieved!')
```

# Dataset Statistics

The threshold value used to categorize yards gained was the median of Yards gained per season in both t1 and t2.

```{r, echo = FALSE}
cat('Summary of Yards Gained in t1:\n')
summary(expanded_data$Yards_t1)

cat('\nSummary of Yards Gained in t2:\n')
summary(expanded_data$Yards_t2)

cat('\n-\t\t-\t\t-',
    '\n\nSummary of Yard Categorizations:\n')

yds_cat_summary <- as.matrix(table(expanded_data[,c("Yards_Category_t1","Yards_Category_t2")]))
dimnames(yds_cat_summary) <- list(t1 = c('At or above median', 'Below median'),
                                  t2 = c('At or above median', '   Below median'))
yds_cat_summary
```

```{r}
cat('Sample size:',
    as.character(dim(expanded_data)[1]),
    'football players\n')

ggplot( expanded_data, aes(x = sapply(Yards_t1, mean, Yards_t2, trim = 0))) +
  geom_histogram( breaks = seq(0,2250, by = 250/2) ) +
  labs(title = 'Histogram of Yards Gained in a Year',
       subtitle = 'Values determined for each player as the average of yards gained in t1 and t2',
       x = 'Mean Amount of Yards Gained by a Player in a Year',
       y = 'Number of Players')

ggplot(expanded_data, aes(ifelse(Played_t3,'Playing','Not Playing'))) +
  geom_bar() +
  labs(title = 'How Many Players Played During their t3?',
       x = 'Play Status of Year t3',
       y = 'Number of Players')
```

```{r}
cat('Correlations between all variables included in maximal model:\n\n')

cor(chronological_data)
heatmap(cor(chronological_data),
        main = 'Heatmap of Correlations',
        Rowv = NA, Colv = NA)
```


# Comparison Statistics

## Summary Statistics

```{r}
cat(' OUTPUT: Maximal Model Statistics\n\n')
print(results_matrix_max)

cat('\n-\t\t-\t\t-\n\n',
    'OUTPUT: Minimal Model Statistics\n\n')
print(results_matrix_min)
```

## Complete Statistics: Maximal Model

```{r}
for (i in 1:length(a_bar_combos)) {
  a_bar_input <- a_bar_combos[[i]]
  
  cat('\nOUTPUT: Maximal Model\n\t(abar =',
      row.names(results_matrix_max)[i], ')\n\n')
  
  print(results_list_max[[i]])
  
  if (i < length(a_bar_combos)) {
    cat('-\t\t-\t\t-\n')
  }
  
}
```

## Complete Statistics: Minimal Model

```{r}
for (i in 1:length(a_bar_combos)) {
  a_bar_input <- a_bar_combos[[i]]
  
  cat('OUTPUT: Minimal Model\n\t(abar =',
      row.names(results_matrix_max)[i], ')\n\n')
  
  print(results_list_min[[i]])
  
  if (i < length(a_bar_combos)) {
    cat('-\t\t-\t\t-\n')
  }
  
}
```
